Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

@@

@@

@@

% sec: test_on_a_synthetic_stream (end)

@@

    Having successful applied the modeling framework to a mock stream,
    we now apply our density modeling approach to the stellar stream GD-1.
    We
    discuss the data selection in \autoref{sub:results_gd1:data},
    model specifics in \autoref{sub:results_gd1:model},
    and the results in \autoref{sub:results_gd1:results}.

>>>>

    \subsection{Data Simulation} \label{sub:results_mock:data}

@@

    \subsection{Model Specification} \label{sub:resultes_mock:model}

@@

    \subsection{Trained Density Model} \label{sub:results_mock:results}

@@

% sec: results  (end)

@@

    Having successful applied the density modeling framework to a
    mock stream, we now apply the method to the stellar stream GD-1.
    % TODO: some reiteration on the importance of GD-1
    We
    discuss the data selection in \autoref{sub:results_gd1:data},
    model specifics in \autoref{sub:results_gd1:model},
    and the results in \autoref{sub:results_gd1:results}.
